The Resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-05-09 paper.tex
Changed the sty file to Revip, cleaned up the look of the paper.

\documentclass[aps,rmp,twocolumn,amsmath,amssymb,nofootinbib,superscriptaddress]{revtex4}

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage[pdftex]{graphicx}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}
\usepackage[dvipsnames]{xcolor}

@@

\begin{document}

\bibliographystyle{apsrev}

@@

\title{The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications}

@@

\author{Si-Hui Tan}
\email[]{sihui\_tan@sutd.edu.sg}
\affiliation{Singapore University of Technology and Design, Singapore University of Technology and Design, 8 Somapah Rd, Singapore 487372}
\affiliation{Centre for 
Quantum Technologies, National University of Singapore, Block S15, 3 Science Drive 2, Singapore 117543, Singapore}
\author{Peter P. Rohde}
\email[]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Software \& Information (CQSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

\date{\today}

\frenchspacing

%
% Abstract
%

\begin{abstract}
\end{abstract}

\maketitle

\tableofcontents

@@

\subsubsection{Polarisation}

@@

\subsubsection{Dual-rail}

@@

\subsubsection{Time-bins}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{reck}
\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.6\columnwidth]{cluster_state}
\caption{The representation of cluster states as a graph. Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on CPHASE gates, the ordering of which is irrelevant.} \label{fig:cluster}	
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.7\columnwidth]{fusion}
\caption{Fusion gates for joining smaller cluster states into larger ones. Both require only a single polarising beamsplitter, and waveplates. The type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, creating an edge between the remaining graphs. The type-I gate consumes one fewer photon, but requires number-resolved detection on the detected mode. The type-II gate requires only on/off photodetection, but consumes an additional photon. Thus, the type-I gate can be employed to fuse two Bell pairs into a 3-qubit cluster state, whereas the type-II gate will only grow clusters when beginning with at least 3 qubits per cluster.} \label{fig:fusion}	
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{full_architecture}
\caption{A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train. The source prepares the temporally encoded pulse-train, with time-bin separation $\tau$. The pulse-train then enters a dual-loop configuration. The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the number of optical modes). The architecture is controlled via three dynamically controlled beamsplitters. The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, keep it within the outer loop for the required duration, and then couple out of the outer loop, yielding the transformed pulse-train. The central beamsplitter must be able to implement arbitrary classically-controlled beamsplitter operations.} \label{fig:FL_arch}	
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.7\columnwidth]{PBS_TB}
\caption{Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train. The PBS completely reflects (transmits) the vertical (horizontal) polarisations. The evolution of the four logical basis states, and their respective outputs, are shown explicitly. Writing out this PBS transformation in matrix form yields a permutation. Taking this permutation and relabelling the modes, we obtain the time-bin transformation shown underneath -- a simple swap of two of the four time-bins.} \label{fig:PBS_TB}	
\end{figure}

@@

 \begin{figure}[!htb]
\includegraphics[width=0.7\columnwidth]{phE}
\caption{A schematic diagram of the Mach-Zehnder interferometer comprising of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two paths.} \label{fig:MZ}	
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{MORDOR}
\caption{Architecture of the quantum Fourier transform interferometer for metrology using single-photon states. QFT: Quantum Fourier transform circuit, and $\varphi_k=(k-1)\varphi$. Single photons are injected into the input modes on the left-hand-side, and a $N$-fold coincidence measurement is conducted at the output on the right-hand-side.} \label{fig:MORDOR}	
\end{figure}

@@

\begin{acknowledgments}
P.P.R. is funded by an ARC Future Fellowship (project FT160100397). This research was supported in part by the Singapore National Research Foundation under NRF Award No. NRF-NRFF2013-01. ST acknowldeges support from the Air Force Office of Scientific Research under AOARD grant FA2386-15-1-4082.

\end{acknowledgments}

@@

\bibliography{paper}

>>>>

%\documentclass[aps,rmp,twocolumn,amsmath,amssymb,nofootinbib,superscripta
%ddress]{revtex4}
\documentclass[times,final]{elsarticle}
\usepackage{revip}
\usepackage{framed,multirow}
\usepackage{hyperref,mathrsfs,amsmath,amssymb,url,latexsym}

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage{graphicx}

%\usepackage[colorlinks]{hyperref}
\usepackage[dvipsnames]{xcolor}

@@

\definecolor{newcolor}{rgb}{.8,.349,.1}

\journal{Reviews in Physics}

\begin{document}
\verso{Tan and Rohde}

\begin{frontmatter}

@@

\title{The Resurgence of the linear optics interferometer --- recent advances \& applications}

@@

\author[1,2]{Si-Hui \snm{Tan}}

\author[3]{Peter P. \snm{Rohde}\corref{cor1}}
\cortext[cor1]{Corresponding author: dr.rohde@gmail.com ;http://
www.peterrohde.org}

\address[1]{Singapore University of Technology and Design, Singapore 
University of Technology and Design, 8 Somapah Rd, Singapore 487372}
\address[2]{Centre for 
Quantum Technologies, National University of Singapore, Block S15, 3 
Science Drive 2, Singapore 117543, Singapore}
\address[3]{Centre for Quantum Software \& Information (CQSI), Faculty 
of Engineering \& Information Technology, University of Technology 
Sydney, NSW 2007, Australia}

\received{}
\finalform{}
\accepted{}
\availableonline{}
\communicated{}

\begin{abstract}
%%%
Please Type your abstract here. Type your abstract here. Type your abstract
here. Type your abstract here. Type your abstract here. Type your
abstract here. Type your abstract here. Type your abstract here. Type
your abstract here. Type your abstract here. Type your abstract here.
Type your abstract here. Type your abstract here.Type your abstract here. 
Type your abstract here. Type your abstract here. Type your abstract here. 
Type your abstract here. Type your abstract here. Type your abstract here.

Please Type your abstract here. Type your abstract here. Type your abstract
Please Type your abstract here. Type your abstract here. Type your abstract
here. Type your abstract here. Type your abstract here. Type your
abstract here. Type your abstract here. Type your abstract here. Type
your abstract here. Type your abstract here. Type your abstract here.
Type your abstract here. Type your abstract here.
Please Type your abstract here. Type your abstract here. 
Type your abstract here.
%%%%
\end{abstract}

\begin{keyword}
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\MSC 41A05\sep 41A10\sep 65D05\sep 65D17
%% Keywords
\KWD Keyword1\sep Keyword2\sep Keyword3
\end{keyword}

\end{frontmatter}

@@

\subsection{Polarisation}

@@

\subsection{Dual-rail}

@@

\subsection{Time-bins}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.7\columnwidth]{reck}
\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.3\columnwidth]{cluster_state}
\caption{The representation of cluster states as a graph. Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on CPHASE gates, the ordering of which is irrelevant.} \label{fig:cluster}	
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.4\columnwidth]{fusion}
\caption{Fusion gates for joining smaller cluster states into larger ones. Both require only a single polarising beamsplitter, and waveplates. The type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, creating an edge between the remaining graphs. The type-I gate consumes one fewer photon, but requires number-resolved detection on the detected mode. The type-II gate requires only on/off photodetection, but consumes an additional photon. Thus, the type-I gate can be employed to fuse two Bell pairs into a 3-qubit cluster state, whereas the type-II gate will only grow clusters when beginning with at least 3 qubits per cluster.} \label{fig:fusion}	
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.5\columnwidth]{full_architecture}
\caption{A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train. The source prepares the temporally encoded pulse-train, with time-bin separation $\tau$. The pulse-train then enters a dual-loop configuration. The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the number of optical modes). The architecture is controlled via three dynamically controlled beamsplitters. The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, keep it within the outer loop for the required duration, and then couple out of the outer loop, yielding the transformed pulse-train. The central beamsplitter must be able to implement arbitrary classically-controlled beamsplitter operations.} \label{fig:FL_arch}	
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.4\columnwidth]{PBS_TB}
\caption{Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train. The PBS completely reflects (transmits) the vertical (horizontal) polarisations. The evolution of the four logical basis states, and their respective outputs, are shown explicitly. Writing out this PBS transformation in matrix form yields a permutation. Taking this permutation and relabelling the modes, we obtain the time-bin transformation shown underneath -- a simple swap of two of the four time-bins.} \label{fig:PBS_TB}	
\end{figure}

@@

 \begin{figure}[!htb]
 \centering
\includegraphics[width=0.4\columnwidth]{phE}
\caption{A schematic diagram of the Mach-Zehnder interferometer comprising of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two paths.} \label{fig:MZ}	
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.5\columnwidth]{MORDOR}
\caption{Architecture of the quantum Fourier transform interferometer for metrology using single-photon states. QFT: Quantum Fourier transform circuit, and $\varphi_k=(k-1)\varphi$. Single photons are injected into the input modes on the left-hand-side, and a $N$-fold coincidence measurement is conducted at the output on the right-hand-side.} \label{fig:MORDOR}	
\end{figure}

@@

\section*{Acknowledgments}
P.P.R. is funded by an ARC Future Fellowship (project FT160100397). This research was supported in part by the Singapore National Research Foundation under NRF Award No. NRF-NRFF2013-01. ST acknowldeges support from the Air Force Office of Scientific Research under AOARD grant FA2386-15-1-4082.

@@

\section*{References}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{paper}
